%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page 
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%		
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}  

% Default font is the helvetica postscript font
\usepackage{helvet}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\usepackage{hyperref}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{RAMI MASRI}
\par 
% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile 
\par
\address{\\ Ph.D. Candidate, Rice University \\ Department of Computational and Applied Mathematics \\  Duncan Hall 2108, \\ \href{https://ramimasri.github.io}{https://ramimasri.github.io}}
\address{\\ rami.masri@rice.edu\\ 1333 Old Spanish Trail\\  (832) 938-8214 \\Houston, TX 77054}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{Ph.D., Computational and Applied Mathematics}, May 2022 (expected)\\
Rice University, Houston, TX \\ 
Advisor: Prof. Beatrice Riviere 
\par \textbf{Graduate Certificate in Teaching and Learning}, December 2022 (expected)\\
Rice University Center of Teaching Excellence, Houston, TX 
\par
\textbf{M.A., Computational and Applied Mathematics}, May 2019 \\
Rice University, Houston, TX \\ 
Advisor:  Prof. Beatrice Riviere 
%Thesis: Derivation and Numerical Simulation of Oxygen Transport in Blood Vessels. 
\par
\textbf{B.S., Mathematics}, with high distinction, May 2017\\
Lebanese American University, Beirut, Lebanon 
%-----------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%	RESEARCH SECTION
%-------------------------------------------------------------------------------
\section{RESEARCH}
\par
\textbf{Numerical Analysis of Discontinuous Galerkin Methods} \\
Cahn–Hilliard–Navier–Stokes equations \\ 
 Incompressible Navier--Stokes equations   \\ 
 Elliptic problems with a Dirac line source \\ 
Nonlinear convection diffusion equations 

\par 
\textbf{Mathematical Modeling} \\
 Blood flow and solute transport in vessel networks
 
 % Modify the format of each position
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%--------------------------------------------------------------------

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	TEACHING SECTION
%-------------------------------------------------------------------------------
\section{TEACHING}
\par
\textbf{Teaching Assistant}
\\ \textit{CAAM 336},  Differential equations in science and engineering \\ 
%Conducted recitation sessions and held office hours  \\ 
Rice University, Department of Computational and Applied Mathematics  \\ 
Fall 2019, Spring 2020, Fall 2021  \\ 
%\textit{Grader}, CAAM 336,  Fall 2017 - Spring 2018, Fall 2020 - Spring 2021.  \\ 
%\textit{Grader}, CAAM 453: Numerical Analysis 1, Fall 2018
\\  \textit{MTH 101--102}, Introductory calculus courses\\ Lebanese American University,  Department of Computer Science and Mathematics \\ 
Fall 2016, Spring 2017 \\  \\ 
%-------------------------------------------------------------------------------
\textbf{Grader} 
\\ CAAM 336,   Differential equations in science and engineering, \\ 
Rice University, Department of Computational and Applied Mathematics  \\ 
 Fall 2017, Spring 2018 \\  \\ 
 CAAM 453, Numerical Analysis I \\
 Rice University, Department of Computational and Applied Mathematics  \\ 
  Fall 2018
%-------------------------------------------------------------------------------
%	PUBLICATIONS
%-------------------------------------------------------------------------------
\section{PAPERS}
\par R. Masri, C. Liu, B. Riviere. Improved velocity and pressure error estimates for a discontinuous Galerkin pressure correction scheme. \textit{In preparation}, 2021 
\par R. Masri, C. Liu, B. Riviere. A discontinuous Galerkin pressure correction scheme for the incompressible Navier-Stokes equations: stability and convergence. \textit{Submitted},  arXiv: 2109.10999,\,2021
\par R. Masri, C. Puelz, B. Riviere. A discontinuous Galerkin method for blood flow and solute transport in one dimensional vessel networks. 
 \textit{Communications on Applied Mathematics and Computation}, p. 1-30, doi:10.1007/s42967-021-00126-5, 2021
\par
R. Masri, C. Puelz, B. Riviere. A reduced model for solute transport in compliant blood vessels with arbitrary axial velocity profile. \textit{International Journal of Heat and Mass Transfer}, 176, 121379, doi: 10.1016/j.ijheatmasstransfer.2021.121379, 2021

\section{REPORTS} 
\par N. Berre, G. Castro, H.  Kjeldsberg, R. Masri, and I. Gjerde. A computational study on flow instabilities in aneurysms. \textit{SSCP Simula SpringerBrief on Computing: Reports on Computational Physiology} (to appear), 2021 
\par  The open source implementation of the above study can be found here: \\  
Kjeldsberg, H., Masri, R., Berre, N., Castro, G., and Gjerde, I. \,\,  Flowinstabilities. \\ https://doi.org/10.5281/zenodo.5296829, Aug. 2021

\section{THESES}
\par  R. Masri. Derivation and numerical simulation of oxygen transport in blood vessels. \textit{ Master of Arts Thesis, Rice University}, 2019

\section{TALKS}
Stability and convergence of high order discontinuous Galerkin methods for incompressible flows. \textit{SIAM Texas Louisiana Annual Meeting (Upcoming)}, November 2021 
\par One dimensional models of solute transport and blood flow: derivation and numerical simulation. \textit{SIAM Conference on Computational Science and Engineering}, March  2021
\par Derivation and simulation of blood flow and solute transport models in one dimensional vessel networks.\textit{ SIAM Texas Louisiana Annual Meeting}, October 2020
\par One dimensional models of solute transport and blood flow in vessel networks. \textit{Departmental Graduate Student Seminar at Rice University}, October 2020
\par Derivation and simulation of a reduced solute transport model in compliant blood vessels with a general velocity field.  \textit{Accepted in SIAM Life Sciences}, June 2020. Cancelled due to Covid
\par 
Discontinuous Galerkin methods for blood flow and solute transport models.\textit{ Finite Element Rodeo at Baylor University}, March 2020
\par 
 Reduced models of blood flow and solute transport. \textit{Departmental Graduate Student Seminar at Rice University}, January 2020
\section{AWARDS}
\textbf{Student Travel Award}, SIAM Conference on Computational Science and Engineering, 2021 
\par
\textbf{Alan Weiser Memorial Travel Award}, Rice University, 2020
\par 
\textbf{Fulbright Winner}, U.S. Embassy in Beirut,  2017
\par
\textbf{Full Merit Scholarship}, Lebanese American University, 2015-2017  \par
\textbf{National Public Speaking Contest  Winner}, English Speaking Union, 2016 

\section{MENTORSHIP}
\textbf{Graduate Student Mentor} \\
Rice University, Department of Computational and Applied Mathematics, Fall 2021  \par 
\textbf{Trainer}  \\ 
Lebanese American University, Model Arab League, Fall 2018    
\section{LEADERSHIP} \textbf{Graduate Liaison}\\
Center of Teaching Excellence, Fall 2021   
\par \textbf{Vice President} \\
SIAM Student Chapter, Rice University, Fall 2021 
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-----------------------------------------------------------------------------

\section{COMPUTER\\SKILLS}

\textbf{Languages} \\ 
Python, C, C\texttt{++} 
\par 
\textbf{Software}: \\ MATLAB, \LaTeX, FEniCS

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	MEMBERSHIPS
%-------------------------------------------------------------------------------
\section{MEMBERSHIPS}

\par
SIAM Student Chapter at Rice University \par 

AWM Student Chapter at Rice University
\section{LANGUAGES} 
English,  Arabic 
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	EXTRACURRICULARS	
%------------------------------------------------------------------------------

\end{resume}
\end{document}